Linear and Differential Cryptanalysis of DES

### 2009-03-09 talk/draft1.tex
Final Updates

\vspace{3mm}
\pause For a full 16-round DES, the best approximation has bias $\sim 1.19\times 10^{-22}$, thus we would need on the order of $2^{47}$ plaintext-ciphertext pairs.
\end{frame}

>>>>

\vspace{3mm}
\pause For a full 16-round DES, the best approximation has bias $\sim 1.19\times 10^{-22}$, thus we would need on the order of $2^{47}$ plaintext-ciphertext pairs.\\
\vspace{3mm}
The 15-round best expression has the following form:
\[ P_L[8] \oplus P_L[14] \oplus P_L[25] \oplus P_R[16] \oplus P_R[20] \oplus \]
\[  U_{16L}[17] \oplus U_{16R}[3] \oplus U_{16R}[8] \oplus U_{16R}[14] \oplus U_{16R}[25] = \Sigma K \]
\end{frame}
